### 2013-04-10 MSteenhagen-CV.tex
AOS/AOC adjustment
Blocked out 2012 response to Lamb (to keep it two pages)
Fixed typo in CV (MPhil Stud completion year)
Reformulated dissertation focus

\ind Dissertation on the nature of human experience of pictorial representation. Supervisor: Prof. Mark Eli Kalderon.

@@

\ind Philosophy of Psychology; Philosophy of Mind \amper Language; Aesthetics.

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. Philosophy; Political Philosophy.

@@

\ind 2012. MPhil Stud. research student. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

\ind 2012. ``How the five die: Response to Lamb.'' University College London, 2012 Graduate Conference in Philosophy. (Response paper.)

>>>>

\ind Dissertation on the perceptual nature of pictorial representation.\\ Supervisor: Prof. Mark Eli Kalderon.

@@

\ind Philosophy of psychology; Philosophy of perception; Aesthetics.

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. philosophy; Philosophy of language.

@@

\ind 2011. MPhil Stud. research student. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

% \ind 2012. ``How the five die: Response to Lamb.'' University College London, 2012 Graduate Conference in Philosophy. (Response paper.)
